Comparison of Terrain Following and Cut Cell Grids with a Non-Hydrostatic Model

### 2015-02-02 msc-publication.tex
put advection contours into their own PDF, include in main PDF

Analysis:
\begin{itemize}
	\item Upwind-biased cubic is qualitatively better than Sch\"ar's 4th order leapfrog on BTF grid (figure~\ref{fig:advection})
	\item SnapCol error, min and max is almost identical to noOrography (unsurprisingly) (table~\ref{tab:advection})  This agrees with \citet{good2014}
	\item SLEVE error, min and max are part-way between BTF and noOrography (again, unsurprisingly)
	\item noOrography, BTF and SLEVE min and max comparable to \citet{schaer2002}
	\item Conclusion: advection more accurate on more regular grids, but nevertheless satisfactory on all grids
\end{itemize}

\begin{figure}
	btf-cubicUpwindCPCFit-divFree \\
	\input{../advectTracer-horizontal-btf-cubicUpwindCPCFit-divFree/tracer-contour}
	\input{../advectTracer-horizontal-btf-cubicUpwindCPCFit-divFree/error-contour}

	schaer-4thorder \\
	\includegraphics[height=1.5in]{schaer-btf-4thorder.png}
	\includegraphics[height=1.5in]{schaer-btf-4thorder-error.png}

	\TODO{also include SnapCol results}
	\TODO{check error contours are correct (0.01?)}
%
	\caption{Comparing our BTF cubicUpwindCPCFit result with Schaer's 4th order result}
	\label{fig:advection}
\end{figure}

@@

\section{Conclusions}
\begin{enumerate}
	\item BTF grid isn't as bad as people say it is.  We found that:
	\begin{itemize}
		\item Upwind-biased cubic advection scheme accurately advects a tracer in non-divergent flows (Figure~\ref{fig:advection}, Table~\ref{tab:advection})
		\item spurious vertical velocities are small in resting atmosphere (Figure~\ref{fig:resting})
		\item gravity waves results visually as good as reference solution from \citet{melvin2010} (figure~\ref{fig:gw-w})
	\end{itemize}

>>>>

Analysis:
\begin{itemize}
	\item Upwind-biased cubic is qualitatively better than Sch\"ar's 4th order leapfrog on BTF grid (figure~\ref{fig:advection-tracer})
	\item SnapCol error, min and max is almost identical to noOrography (unsurprisingly) (table~\ref{tab:advection})  This agrees with \citet{good2014}
	\item SLEVE error, min and max are part-way between BTF and noOrography (again, unsurprisingly)
	\item noOrography, BTF and SLEVE min and max comparable to \citet{schaer2002}
	\item Conclusion: advection more accurate on more regular grids, but nevertheless satisfactory on all grids
\end{itemize}

\begin{figure}
	\centering
	\includegraphics{../msc-publication-fig-advection-tracer/fig-advection-tracer.pdf}

%	btf-cubicUpwindCPCFit-divFree \\
%	\input{../advectTracer-horizontal-btf-cubicUpwindCPCFit-divFree/error-contour}

%	schaer-4thorder \\
%	\includegraphics[height=1.5in]{schaer-btf-4thorder-error.png}
%
	\caption{Horizontally advected tracer contours at $t = \SI{0}{\second}$, \SI{5000}{\second} and \SI{10000}{\second}.  \TODO{identify subfigures}  Contour intervals are every 0.1.}
	\label{fig:advection-tracer}
\end{figure}

\begin{figure}
	\centering
	\caption{Errors in horizontal tracer advection at $t = \SI{10000}{\second}$.  \TODO{identify subfigures}  Contour intervals are every 0.01 with negative contours denoted by dashed lines.}
	\label{fig:advection-error}
\end{figure}

@@

\section{Conclusions}
\begin{enumerate}
	\item BTF grid isn't as bad as people say it is.  We found that:
	\begin{itemize}
		\item Upwind-biased cubic advection scheme accurately advects a tracer in non-divergent flows (Figure~\ref{fig:advection-tracer}, \ref{fig:advection-error}, Table~\ref{tab:advection})
		\item spurious vertical velocities are small in resting atmosphere (Figure~\ref{fig:resting})
		\item gravity waves results visually as good as reference solution from \citet{melvin2010} (figure~\ref{fig:gw-w})
	\end{itemize}
